Backbone-Store: An API for Automating Local Caching of Web Application Data

### 2012-05-21 paper/paper.tex
fixed typos

\begin{abstract}
Efficiently storing web application data in the client's browser was a
challenging task until the recent HTML5 specification. Web applications that
require fetching the same data that has been previously fetched from a server
can see an improved load time by storing this old data in the client's browser,
requiring only the new data to be retrieved from the server. For our project,
we extended Backbone.js to allow a web developer to easily store and reload a
web application's data using the HTML5 localStorage API. We analyze three
simple applications to study the performance characteristics of loading large
douments, medium-sized emails, and small notes from both the localStorage on
the client's browser and on the server. We find that localStorage performs
faster than loading the same data from th server. This time difference
increases for larger quantities of the same type of item. Since the threshold
for users perceiving lag is about 100 milliseconds, we show that there are
real-world usecases where loading data from a server would cause users to
percieve lag, while loading the same data from localStorage would be percieved
as instantaneous.
\end{abstract}

@@

Currently, for a web programmer to store data on the client side while using
Backbone.js, he/she would need to write a custom storage solution to save the
data from each of their models and/or collections to HTML5's localStorage or
another local storage option. Backbone-store simplifies the process of saving
information from a model or collection such that it can be reloaded into the
models and collections the next time the web application starts. With a few new
methods added to the Model and Collection objects, a web developer can choose
when a copy of a model's or collection's data should be stored, and when to
load saved data back into the application's models or collections. There is
also a choice of how the data is stored for collections of models. All models
can be stored as a bundle under one key in the localStorage, or they can be
stored individually, with each model under its own key in the localStorage.
This provides flexibility for different usecases where one option may be
significantly better than the other one depending on the number of items and
the amount of data being stored.

@@

Second, we conduct a performance evaluation of load and update times for data
stored locally (using the aforementioned two strategies) compared to data
stored remotely for three types of web applications that differ in data size
per item (70 bytes, 900 bytes, 3200 bytes) and data quantity (10, 50, 100, 200,
300 items per collection) and highlight conditions where local storage is most
advantageous.

We find that our API provides superior load and update performance for data
stored locally vs.\ remotely under all data size and quantity conditions except
for the case of loading many small items. Furthermore, we find that our
implementation of local caching exhibits the greatest speedup when data is
stored using the first strategy, with one key-value pair per collection. This
suggests that local caching is most advantageous for applications that load
data of larger size, and moderate to large quantity.

@@

To evaluate the benefits of Backbone-store, we build three test applications to
understand how our solution handled three different sizes of items requiring
storage. To test large items that might represent a document, we used five
paragraphs of lorem-ipsum, totalling 3265 characters per item. To examine
medium size items such as emails, we used one paragraph of lorem-ipsum,
totallying 905 characters per item. To examine smaller items such as personal
notes, we used a short string of 70 characters. These character lengths are the
length of the JSON string that represents each item. The three applications
performed the same task: load some number of a particular type of item from
localStorage and from the server, separated by a delay so as not to overlap in
execution and skew the load time, and record the load time.

Each of the three web applications records how long it takes the application to
load the data for each of the three test applications. For the time it takes to
load data from the server, the timer is started just before an Ajax request
asks the server for the data. When the data returns from the server, it is
loaded into a Backbone.Collection object, and the timer is stopped after this
is complete. To record the time to load the same data from localStorage, the
timer is started when just before the \verb=loadFromStore= method is called by
a collection. The data is then fetched from localStorage and parsed from a JSON
string into an array of objects, which is then added to the collection before
finally stopping the timer.

@@

Finally, we also tested update times for our two persistence strategies. We did
this by creating collections with different numbers of items, and measuring the
time to save each collection to localStorage. Also, to test different save-time
characteristics of our different persistence strategies, we measured the time
to resave the collection after adding one model. We predict that the
one-key-per-model persistence strategy will allow faster updates, by making it
possible to save only those models that were changed or added since the last
save.

@@

We load the data from each application in varying quantities (10, 50, 100, 200,
300 items per follection) and show that local caching performs faster than data
loaded from the server (except for collections of small items, where the gain
becomes negligible, most likely because of the overhead involved in retrieving
items from the local store).

@@

Loading large items, such as documents, from the local storage (shown in Figure
\ref{fig:line}A) gives the results that we expect. Load times for both
persistence strategies, and from the server, grow linearly with the number of
items in the collection, and thus with the amount of data retrieved. Both local
persistence methods are faster than retrieving items from the local storage;
the one-key-per-model method is slightly slower than the one-key-per-collection
method due to the additional overhead of retrieving each model from the local
storage separately.

>>>>

\begin{abstract}
Efficiently storing web application data in the client's browser was a
challenging task until the recent HTML5 specification. Web applications that
require fetching the same data that has been previously fetched from a server
can see an improved load time by storing this old data in the client's browser,
requiring only the new data to be retrieved from the server. For our project,
we extended Backbone.js to allow a web developer to easily store and reload a
web application's data using the HTML5 localStorage API. We analyze three
simple applications to study the performance characteristics of loading large
documents, medium-sized emails, and small notes from both the local storage on
the client's browser and on the server. We find that local storage performs
faster than loading the same data from the server. This time difference
increases for larger quantities of the same type of item. Since the threshold
for users perceiving lag is about 100 milliseconds, we show that there are
real-world use cases where loading data from a server would cause users to
perceive lag, while loading the same data from localStorage would be perceived
as instantaneous.
\end{abstract}

@@

Currently, for a web programmer to store data on the client side while using
Backbone.js, he/she would need to write a custom storage solution to save the
data from each of their models and/or collections to HTML5's localStorage or
another local storage option. Backbone-store simplifies the process of saving
information from a model or collection such that it can be reloaded into the
models and collections the next time the web application starts. With a few new
methods added to the Model and Collection objects, a web developer can choose
when a copy of a model's or collection's data should be stored, and when to
load saved data back into the application's models or collections. There is
also a choice of how the data is stored for collections of models. All models
can be stored as a bundle under one key in the localStorage, or they can be
stored individually, with each model under its own key in the localStorage.
This provides flexibility for different use cases where one option may be
significantly better than the other one depending on the number of items and
the amount of data being stored.

@@

Second, we conduct a performance evaluation of load times for data
stored locally (using the aforementioned two strategies) compared to data
stored remotely for three types of web applications that differ in data size
per item (70 bytes, 900 bytes, 3200 bytes) and data quantity (10, 50, 100, 200,
300 items per collection) and highlight conditions where local storage is most
advantageous.

We find that our API provides superior load performance for data
stored locally vs.\ remotely under all data sizse and quantity conditions except
for the case of loading many small items. Furthermore, we find that our
implementation of local caching exhibits the greatest speedup when data is
stored using the first strategy, with one key-value pair per collection. This
suggests that local caching is most advantageous for applications that load
data of larger size, and moderate to large quantity.

@@

To evaluate the benefits of Backbone-store, we built three test applications to
understand how our solution handled three different sizes of items requiring
storage. To test large items that might represent a document, we used five
paragraphs of Lorem ipsum, totaling 3265 characters per item (~3200 bytes). To examine
medium size items such as emails, we used one paragraph of Lorem ipsum,
totaling 905 characters per item (~900 bytes) . To examine smaller items such as personal
notes, we used a short string of 70 characters (~70 bytes). These character lengths are the
length of the JSON string that represents each item. The three applications
performed the same task: 
\begin{enumerate}
\item load some number of a particular type of item (e.g., doc, email, note) from
local storage
\item load some number of a particular type of item (e.g., doc, email, note) from the server
\item record the load time.
\end{enumerate}

Note that 1) and 2) are separated by a delay so as not to overlap in
execution and skew the load time.

Each of the three web applications records how long it takes the application to
load the data for each of the three test applications. For the time it takes to
load data from the server, the timer is started just before an Ajax request
asks the server for the data. When the data returns from the server, it is
loaded into a Backbone.Collection object, and the timer is stopped after this
is complete. To record the time to load the same data from local storage, the
timer is started when just before the \verb=loadFromStore= method is called by
a collection. The data is then fetched from local storage and parsed from a JSON
string into an array of objects, which is then added to the collection before
finally stopping the timer.

@@

Finally, we also tested update times for our two local storage strategies. We did
this by creating collections with different numbers of items, and measuring the
time to save each collection to local storage. Also, to test different save-time
characteristics of our different persistence strategies, we measured the time
to resave the collection after adding one model. We predict that the
one-key-per-model local storage strategy will allow faster updates, by making it
possible to save only those models that were changed or added since the last
save.

@@

We load the data from each application in varying quantities (10, 50, 100, 200,
300 items per collection) and show that local caching performs faster than data
loaded from the server (except for collections of small items, where the gain
becomes negligible, most likely because of the overhead involved in retrieving
items from the local store).

@@

Loading large items, such as documents, from the local storage (shown in Figure
\ref{fig:line}A) gives the results that we expect. Load times for both
local storage strategies, and from the server, grow linearly with the number of
items in the collection, and thus with the amount of data retrieved. Both local
persistence methods are faster than retrieving items from the local storage;
the one-key-per-model method is slightly slower than the one-key-per-collection
method due to the additional overhead of retrieving each model from the local
storage separately.
